Figure: the scatterblob

### 2022-06-04 R/scatterblob.Rmd
Capitalize y-axis labels for consistency
e.g. `"Low\nintermediate"` -> `"Low\nIntermediate"`

if (plot_format == "pdf") {
  pdf(file = here(outpath, paste0(plot_name, ".pdf")),
      width = 8.25,
      height = 6,
      bg = "white")  
}
if (plot_format == "svg") {
  svg(filename = here(outpath, paste0(plot_name, ".svg")),
      width = 8.25,
      height = 6,
      bg = "white")  
}
if (plot_format == "png") {
  png(file = here(outpath, paste0(plot_name, ".png")),
      width = 8.25,
      height = 6,
      units = "in",
      res = 300,
      bg = "white")  
}
par(xpd = NA,
    mai = c(1.02, 1, 0.82, 4),
    bty="n")
###############################################################
# create the plot background
###############################################################
plot(x = c(0.5, 5.5),
     y = c(0.4, 12.5),
     xlab = "",
     ylab = "",
     col = "white",
     # "hide" the tick labels so we can put some words instead of numbers:
     col.axis = "white",
     tck = 0.02)
title(ylab="Technical difficulty", line=4, cex.lab=1)
title(xlab="Degree of collaborativeness", line= 3.5, cex.lab=1)
###############################################################
# add tick labels
###############################################################
text(x = 1:5,
     y = c(-0.65, rep(-0.7, 4)), 
     cex = 0.7,
     labels = c("Personal", 
                "Lab \nmembers", 
                "Other \nlabs", 
                "EEB \ncommunity", 
                "All \nusers"))
text(x = c(1, 3, 5),
     y = -1.7, 
     labels = c("Low", "Medium", "High"))
# Technical difficulty levels from https://www.londonschool.com/level-scale/
text(x = 0.2,
     y = c(0, 1.5, 3, 4.5, 6, 7.5, 9, 10.5, 12 ), 
     cex = 0.7,
     adj = 1,
     labels = c("Beginner",
                "Elementary", 
                "Low\nintermediate",
                "Pre\nintermediate",
                "Intermediate", 
                "Upper\nintermediate",
                "Pre\nAdvanced",
                "Advanced",
                "Very\nAdvanced"))
###############################################################
# plot scatter blobs on sequential cognitive load
###############################################################
for (i in seq(nrow(my_data))) {
  X0 <- my_data$x1[i]
  X1 <- my_data$x2[i]
  Y <- my_data$y_seq[i]
  if (X0 == X1) {
    X0 <- X0 - 0.01
    X1 <- X1 + 0.01
   }
  segments(x0 = X0,
           x1 = X1,
           y0 = Y,
           col = my_colors[i],
           lwd = 23)
}
###############################################################
# add github uses text
###############################################################
text(x = 5.5,
    y = my_data$y_seq,
    labels = my_data$`Ways to use GitHub`,
    adj = 0,
    col = my_colors)
dev.off()
```

>>>>

if (plot_format == "pdf") {
  pdf(file = here(outpath, paste0(plot_name, ".pdf")),
      width = 8.25,
      height = 6,
      bg = "white")  
}
if (plot_format == "svg") {
  svg(filename = here(outpath, paste0(plot_name, ".svg")),
      width = 8.25,
      height = 6,
      bg = "white")  
}
if (plot_format == "png") {
  png(file = here(outpath, paste0(plot_name, ".png")),
      width = 8.25,
      height = 6,
      units = "in",
      res = 300,
      bg = "white")  
}
par(xpd = NA,
    mai = c(1.02, 1, 0.82, 4),
    bty="n")
###############################################################
# create the plot background
###############################################################
plot(x = c(0.5, 5.5),
     y = c(0.4, 12.5),
     xlab = "",
     ylab = "",
     col = "white",
     # "hide" the tick labels so we can put some words instead of numbers:
     col.axis = "white",
     tck = 0.02)
title(ylab="Technical difficulty", line=4, cex.lab=1)
title(xlab="Degree of collaborativeness", line= 3.5, cex.lab=1)
###############################################################
# add tick labels
###############################################################
text(x = 1:5,
     y = c(-0.65, rep(-0.7, 4)), 
     cex = 0.7,
     labels = c("Personal", 
                "Lab \nmembers", 
                "Other \nlabs", 
                "EEB \ncommunity", 
                "All \nusers"))
text(x = c(1, 3, 5),
     y = -1.7, 
     labels = c("Low", "Medium", "High"))
# Technical difficulty levels from https://www.londonschool.com/level-scale/
text(x = 0.2,
     y = c(0, 1.5, 3, 4.5, 6, 7.5, 9, 10.5, 12 ), 
     cex = 0.7,
     adj = 1,
     labels = c("Beginner",
                "Elementary", 
                "Low\nIntermediate",
                "Pre\nIntermediate",
                "Intermediate", 
                "Upper\nIntermediate",
                "Pre\nAdvanced",
                "Advanced",
                "Very\nAdvanced"))
###############################################################
# plot scatter blobs on sequential cognitive load
###############################################################
for (i in seq(nrow(my_data))) {
  X0 <- my_data$x1[i]
  X1 <- my_data$x2[i]
  Y <- my_data$y_seq[i]
  if (X0 == X1) {
    X0 <- X0 - 0.01
    X1 <- X1 + 0.01
   }
  segments(x0 = X0,
           x1 = X1,
           y0 = Y,
           col = my_colors[i],
           lwd = 23)
}
###############################################################
# add github uses text
###############################################################
text(x = 5.5,
    y = my_data$y_seq,
    labels = my_data$`Ways to use GitHub`,
    adj = 0,
    col = my_colors)
dev.off()
```
